---
title: "Additional_stuff"
author: "Kristina Maceković"
date: "5/12/2020"
output: html_document
---

```{r, echo=FALSE}
# Check working directory
Sys.setlocale("LC_ALL","English")
getwd()
#setwd(paste(getwd(), "/Documents/jobs/jobs2020/lebesgue-test-exercise", sep=""))
```

# Is there a time of day when most subs are created or cancelled?
```{r, import data, echo=FALSE}
subscriptions_dataset = read.csv("./init_data/subscriptions.csv")
subscriptions_dataset$sub_created_h = 
    format(strptime(subscriptions_dataset$created_at, "%Y-%m-%d %H:%M:%S"), "%H")
subscriptions_dataset$sub_cancelled_h = 
    format(strptime(subscriptions_dataset$cancelled_at, "%Y-%m-%d %H:%M:%S"), "%H")
```

## Created
```{r}
when_created = data.frame(table(subscriptions_dataset$sub_created_h)/nrow(subscriptions_dataset))
names(when_created) = c("Hour", "Percent of all subs")
when_created[order(-when_created$`Percent of all subs`),]
barplot(when_created$`Percent of all subs`, names.arg = when_created$Hour, main="When are subs created during the day?")
```


## Cancelled
```{r}
when_cancelled = data.frame(table(subscriptions_dataset$sub_cancelled_h)/nrow(subscriptions_dataset))
names(when_cancelled) = c("Hour", "Percent of all subs")
when_cancelled[order(-when_cancelled$`Percent of all subs`),]
barplot(when_cancelled$`Percent of all subs`, names.arg = when_created$Hour, main="When are subs cancelled during the day?")
```

I don't know if this is a reflection of the system or customer behaviour, but there are definitely times of the day when subs are created and cancelled more!



# Address analysis

```{r, import data, echo=FALSE}
orders_dataset = read.csv("./init_data/orders.csv")
```

```{r}
#install.packages("jsonlite")
library(jsonlite)
```

```{r}
orders_with_address = subset(orders_dataset, shipping_address != "NULL")
address = jsonlite::stream_in(textConnection(gsub("\\n", "", orders_with_address$shipping_address)))
```

```{r}
orders_with_address = cbind(orders_with_address, address)
```

```{r}
summary(address)
str(address)
```

```{r}
table(as.factor(address$country))
```

All orders are from the US.


```{r}
avg_sub_pr_province = aggregate(total_price~province, data=orders_with_address,mean)
unique_customers = unique(orders_with_address[c("customer_id", "country", "province")])
state_freq = data.frame(table(as.factor(unique_customers$province))/nrow(unique_customers))
state_freq = state_freq[order(state_freq$Freq),]
state_freq[order(-state_freq$Freq),]
dev.new(height=400,noRStudioGD = TRUE)
barplot(tail(state_freq$Freq,10), horiz = TRUE, names.arg = tail(state_freq$Var1, 10))
```

```{r}
names(state_freq) = c("province", "freq")
state_freq = merge(state_freq, avg_sub_pr_province, by="province")
state_freq$freq = state_freq$freq*100
# freq is for unique customers in the table!
names(state_freq) =c("province", "freq", "average_total_price_of_order")
```

```{r paged.print=FALSE}
#install.packages("ggplot2")
library(ggplot2)
```


```{r}
ggplot(state_freq, aes(freq,average_total_price_of_order)) + geom_text(aes(label=province))
```



# Cancellation Rate per Province analysis
```{r}
unique_customers = unique(orders_with_address[c("customer_id", "province")])
subs = merge(subscriptions_dataset, unique_customers, by="customer_id", all.x=TRUE)
```

## Total per province
```{r}
total_per_province = data.frame(table(subs$province))
names(total_per_province) = c("province", "freq_total")
```

## Status per province
```{r}
install.packages("reshape")
library(reshape)
```


```{r}
cancelled = data.frame(table(subs$province, subs$status))
names(cancelled) = c("province", "status", "freq_status")
cancelled = cast(cancelled, province  ~ status)
```

```{r}
cancelled = merge(cancelled, total_per_province, by="province")
```

```{r}
cancelled$ACTIVE = (cancelled$ACTIVE/cancelled$freq_total)*100
cancelled$CANCELLED = (cancelled$CANCELLED/cancelled$freq_total)*100
cancelled$EXPIRED = (cancelled$EXPIRED/cancelled$freq_total)*100
```

## Avg sub price per province
```{r}
price_per_province = aggregate(subs$price, by=list(subs$province), data=subs, mean)
names(price_per_province) = c("province", "avg_price_of_sub")
cancelled = merge(cancelled, price_per_province, by="province", all.x=TRUE)
```

## Most frequent period
```{r}
mode_period = aggregate(as.factor(subs$order_interval_frequency), by=list(subs$province), function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
})
names(mode_period) = c("province", "period_mode")
cancelled = merge(cancelled, mode_period, by="province", all.x=TRUE)
```

```{r}
write.csv(cancelled, "data_per_province.csv")
```



