---
author: Kristina Macekovic
date: May 2020
title: "Lebesgue data scientist test exercise"
output: 
  html_notebook: 
    fig_caption: yes
    fig_width: 10
    toc: yes
---
# Environment Setup
```{r}
# Check working directory
Sys.setlocale("LC_ALL","English")
getwd()
#setwd(paste(getwd(), "/Documents/jobs/jobs2020/lebesgue-test-exercise", sep=""))
```
# Import Initial Data
```{r}
facebook_ads_dataset = read.csv("./init_data/facebook_ads.csv")
line_items_dataset = read.csv("./init_data/line_items.csv")
orders_dataset = read.csv("./init_data/orders.csv")
subscriptions_dataset = read.csv("./init_data/subscriptions.csv")
```

# Datasets Summaries & Transforms
## Dataset: Facebook Ads
### Structure
```{r}
str(facebook_ads_dataset)
```

### Summary
```{r}
summary(facebook_ads_dataset)
```


### Convert Dates
```{r}
facebook_ads_dataset$date = as.Date(facebook_ads_dataset$date, "%Y-%m-%d")
summary(facebook_ads_dataset)
```
### Add month, year, day, weekday as variables
```{r}
facebook_ads_dataset$year = as.numeric(format(facebook_ads_dataset$date, "%Y"))
facebook_ads_dataset$month = as.numeric(format(facebook_ads_dataset$date, "%m"))
facebook_ads_dataset$day = as.numeric(format(facebook_ads_dataset$date, "%d"))
facebook_ads_dataset$weekday = weekdays(facebook_ads_dataset$date)
summary(facebook_ads_dataset)
```

## Dataset: Line items
### Structure
```{r}
str(line_items_dataset)
```

### Summary
```{r}
summary(line_items_dataset)
```

This datasets seems to contain information on SKUs sold in a ecommerce shop that sells different types of chocolate. "Properties", "Grams", "Images" are all NULL.

## Dataset: Orders
### Structure
```{r}
str(orders_dataset)
```

### Summary
```{r}
summary(orders_dataset)
```

Holds data on orders done through the Shopify platform. *billing address* and *shipping address* are objects!



## Dataset: Subscriptions



### Structure
```{r}
str(subscriptions_dataset)
```

### Summary
```{r}
summary(subscriptions_dataset)
```



### Transforms
```{r}

```



# Question 1: What is the best day of the week to increase advertising spending?
Following metrics should be as high as possible:
```{r}
with(facebook_ads_dataset, tapply(scale(clicks), weekday, summary))
boxplot(scale(clicks) ~ weekday, data=facebook_ads_dataset, main="Scaled Clicks")
abline(a=0, b=0, col="red")
with(facebook_ads_dataset, tapply(scale(ctr), weekday, summary))
boxplot(scale(ctr) ~ weekday, data=facebook_ads_dataset, main="Scaled CTR")
abline(a=0, b=0, col="red")
with(facebook_ads_dataset, tapply(scale(impressions), weekday, summary))
boxplot(scale(impressions) ~ weekday, data=facebook_ads_dataset, main="Scaled impressions")
abline(a=0, b=0, col="red")
with(facebook_ads_dataset, tapply(scale(purchases), weekday, summary))
boxplot(scale(purchases) ~ weekday, data=facebook_ads_dataset, main="Scaled Purchases")
abline(a=0, b=0, col="red")
with(facebook_ads_dataset, tapply(scale(purchases_conversion_value), weekday, summary))
boxplot(scale(purchases_conversion_value) ~ weekday, data=facebook_ads_dataset, main="scaled conversion value")
abline(a=0, b=0, col="red")
```

And following lower:
```{r}
with(facebook_ads_dataset, tapply(scale(cpm), weekday, summary))
boxplot(scale(cpm) ~ weekday, data=facebook_ads_dataset, main="Scaled CPM")
abline(a=0, b=0, col="red")
with(facebook_ads_dataset, tapply(scale(cpc), weekday, summary))
boxplot(scale(cpc) ~ weekday, data=facebook_ads_dataset, main="Scaled CPC")
abline(a=0, b=0, col="red")
with(facebook_ads_dataset, tapply(scale(spend), weekday, summary))
boxplot(scale(spend) ~ weekday, data=facebook_ads_dataset, main="Scaled spend")
abline(a=0, b=0, col="red")
```
We want to maximize this variable:
```{r}
ROI_max = scale((facebook_ads_dataset$clicks+
              facebook_ads_dataset$ctr+
              facebook_ads_dataset$impressions+
              facebook_ads_dataset$reach+
              facebook_ads_dataset$purchases+
              facebook_ads_dataset$purchases_conversion_value)/facebook_ads_dataset$spend)
ROI_min = scale(facebook_ads_dataset$cpc + 
            facebook_ads_dataset$cpm)
facebook_ads_dataset$ROI_max = ROI_max
facebook_ads_dataset$ROI_min = ROI_min
summary(facebook_ads_dataset$ROI_max)
summary(facebook_ads_dataset$ROI_min)
```
ˆ
```{r}
boxplot(ROI_max ~ weekday, data=facebook_ads_dataset, main="ROI_max")
abline(a=mean(facebook_ads_dataset$ROI_max), b=0, col="red")
abline(a=median(facebook_ads_dataset$ROI_max), b=0, col="blue")
boxplot(ROI_min ~ weekday, data=facebook_ads_dataset, main="ROI_min")
abline(a=mean(facebook_ads_dataset$ROI_min), b=0, col="red")
abline(a=median(facebook_ads_dataset$ROI_min), b=0, col="blue")
```

Regression:
```{r}
explanatory = lm(ROI_max ~ weekday, data = facebook_ads_dataset)
summary(explanatory)
tapply(facebook_ads_dataset$ROI_max, facebook_ads_dataset$weekday, summary)
```


```{r}
explanatory_min = lm(ROI_min ~ weekday, data = facebook_ads_dataset)
summary(explanatory_min)
tapply(facebook_ads_dataset$ROI_min, facebook_ads_dataset$weekday, summary)
```

```{r}
with(facebook_ads_dataset, hist(scale(clicks)))
with(facebook_ads_dataset, hist(scale(ctr)))
with(facebook_ads_dataset, hist(scale(impressions)))
with(facebook_ads_dataset, hist(scale(reach)))
```

```{r}
str(as.factor(facebook_ads_dataset$weekday))
```


```{r}
# 1-way ANOVA
fit = aov(ROI_max ~ factor(weekday), data=facebook_ads_dataset)
plot(fit)
summary(fit)
```

# Question 2: How did advertising spending change over time? (Is there a trend?)
```{r}
facebook_ads_dataset$yearMonth = format(facebook_ads_dataset$date, "%Y-%m")
with(facebook_ads_dataset, tapply(spend, yearMonth, summary))
with(facebook_ads_dataset, tapply(spend, yearMonth, mean))
with(facebook_ads_dataset, tapply(spend, yearMonth, sd))

boxplot(spend ~ day, data=facebook_ads_dataset, main="Spend ~ day")
boxplot(spend ~ yearMonth, data=facebook_ads_dataset, main="Spend ~ month")
boxplot(spend ~ year, data=facebook_ads_dataset, main="Spend ~ year")
plot(facebook_ads_dataset$date, facebook_ads_dataset$spend)
subsetBeforeFeb2020 = subset(facebook_ads_dataset, yearMonth<="2020-01")
plot(subsetBeforeFeb2020$date, subsetBeforeFeb2020$spend)
subsetAfterFeb2020 = subset(facebook_ads_dataset, yearMonth > "2020-01")
plot(subsetAfterFeb2020$date, subsetAfterFeb2020$spend)
```

Linear trend:
```{r}
facebook_ads_dataset$daysSinceFirst = as.numeric(facebook_ads_dataset$date - as.Date("2019-01-01"))

modelSpend = lm(spend ~ daysSinceFirst, data=facebook_ads_dataset)
summary(modelSpend)

plot(facebook_ads_dataset$daysSinceFirst, facebook_ads_dataset$spend)
abline(modelSpend, col="red")
```


# Question 3: How do changes in spending affect CTR and CPM?
Since spending has increased with time, I would expect CPM to increase in case of the same number of impressions, or constant in case of linealy increasing impressions.

## Plot of CTR through time:
```{r}
subBefore = subset(facebook_ads_dataset, daysSinceFirst <=250)
subAfter = subset(facebook_ads_dataset, daysSinceFirst >250)
#plot(facebook_ads_dataset$date, scale(facebook_ads_dataset$clicks), main="Clicks")
#plot(facebook_ads_dataset$date, scale(facebook_ads_dataset$impressions), main="Impressions")
plot(facebook_ads_dataset$date, scale(facebook_ads_dataset$ctr), main="CTR")
plot(facebook_ads_dataset$date, scale(facebook_ads_dataset$cpm), main="CPM")
plot(subBefore$date, scale(subBefore$ctr), main="CTR")
plot(subBefore$date, scale(subBefore$cpc), main="CPC")
plot(subAfter$date, scale(subAfter$ctr), main="CTR")
plot(subAfter$date, scale(subAfter$cpc), main="CPC")
```

## Models for CTR and CPC up to Sep:
```{r}
modelCTRBefore = lm(scale(ctr) ~ daysSinceFirst, data = subBefore)
summary(modelCTRBefore)
modelCPCBefore = lm(scale(cpc) ~ daysSinceFirst, data = subBefore)
summary(modelCPCBefore)
```

Model:
```{r}
modelClicks = lm(clicks ~ daysSinceFirst, data=facebook_ads_dataset)
summary(modelClicks)
```


## Plot of CPM through time:
```{r}
# modelCPM = lm(cpm ~ daysSinceFirst, data = subBefore)
# summary(modelCPM)
modelCPM = lm(cpm ~ daysSinceFirst, data = facebook_ads_dataset)
summary(modelCPM)
plot(facebook_ads_dataset$date, facebook_ads_dataset$cpm)
boxplot(facebook_ads_dataset$cpm ~ facebook_ads_dataset$yearMonth)
summary(facebook_ads_dataset$cpm)
```

## Impressions vs time
```{r}
facebook_ads_dataset$daysSinceFirst = as.numeric(facebook_ads_dataset$date - as.Date("2019-01-01"))

model = lm(impressions ~ daysSinceFirst, data=facebook_ads_dataset)
summary(model)

plot(facebook_ads_dataset$daysSinceFirst, facebook_ads_dataset$impressions)
abline(model, col="red")
```

## Spend vs CTR
```{r}
plot(facebook_ads_dataset$spend, scale(facebook_ads_dataset$ctr))
plot(facebook_ads_dataset$spend, scale(facebook_ads_dataset$cpm))
plot(subBefore$spend, scale(subBefore$ctr))
summary(lm(scale(ctr) ~ spend, data=subBefore))
plot(facebook_ads_dataset$spend, facebook_ads_dataset$ctr)
summary(lm(scale(ctr) ~ spend, data=facebook_ads_dataset))
plot(facebook_ads_dataset$spend, facebook_ads_dataset$cpm)
summary(lm(scale(cpm) ~ spend, data=facebook_ads_dataset))
```
