---
author: Kristina Macekovic
year: 2020
title: "Kristina Macekovic solution: Lebesgue data scientist test exercise"
output: html_notebook
---
```{r}
# Check working directory
getwd()
#setwd(paste(getwd(), "/Documents/jobs/jobs2020/lebesgue-test-exercise", sep=""))
```
# Import Initial Data
```{r}
facebooks_ads_dataset = read.csv("./init_data/facebook_ads.csv")
line_items_dataset = read.csv("./init_data/line_items.csv")
orders_dataset = read.csv("./init_data/orders.csv")
subscriptions_dataset = read.csv("./init_data/subscriptions.csv")
```

# Datasets Summaries
## Dataset: Facebook Ads
### Structure
```{r}
str(facebooks_ads_dataset)
# TODO: need to convert dates
```

### Summary
```{r}
summary(facebooks_ads_dataset)
```

This datasets seems to contain data on 483 facebook ad campaigns during 2019 and 2020. Some variables like the account id, one-click purchases contain no info.
*TODO: Convert date to date format*

## Dataset: Line items
### Structure
```{r}
str(line_items_dataset)
```

### Summary
```{r}
summary(line_items_dataset)
```

This datasets seems to contain information on SKUs sold in a ecommerce shop that sells different types of chocolate. "Properties", "Grams", "Images" are all NULL.

## Dataset: Orders
### Structure
```{r}
str(orders_dataset)
```

### Summary
```{r}
summary(orders_dataset)
```

Holds data on orders done through the Shopify platform. *billing address* and *shipping address* are objects!
## Dataset: Subscriptions
### Structure
```{r}
str(subscriptions_dataset)
```

### Summary
```{r}
summary(subscriptions_dataset)
```

Holds data on subsription services. Interesting fields to look at would be 

- *cancellation_reason*
- *cancellation_reason_comment*

(Something simple like a wordcloud or more advanced like NLP analysis)