---
title: "Average length of subscription"
author: "Kristina Maceković"
date: "5/6/2020"
output: html_document
---
# Environment Setup
```{r, enviroment setup}
# Check working directory
Sys.setlocale("LC_ALL","English")
getwd()
#setwd(paste(getwd(), "/Documents/jobs/jobs2020/lebesgue-test-exercise", sep=""))
```




# Import Subscription Data
```{r}
subscriptions_dataset = read.csv("./init_data/subscriptions.csv")
```

# Structure and Summary
```{r}
str(subscriptions_dataset)
summary(subscriptions_dataset)
```

How many customers have subscriptions:
```{r}
num_customers_with_sub = length(unique(subscriptions_dataset$customer_id))
num_customers_with_sub
```

How many subs there are in total:
```{r}
num_subs = nrow(subscriptions_dataset)
num_subs
```


Average number of subs per customer:
```{r}
num_subs_per_customer = data.frame(table(subscriptions_dataset$customer_id))
names(num_subs_per_customer) = c("customer_id", "num_subs_total")
```

```{r}
subscriptions_dataset = merge(x=subscriptions_dataset, y=num_subs_per_customer, by="customer_id", all.x = TRUE)
```

```{r}
summary(subscriptions_dataset$num_subs_total)
boxplot(subscriptions_dataset$num_subs_total)
```

# Proportions of active, cancelled and expired Subs
```{r}
str(subscriptions_dataset$status)
summary(subscriptions_dataset$status)/nrow(subscriptions_dataset)
```

```{r}
expired_subs = subset(subscriptions_dataset, status == "EXPIRED")
nrow(expired_subs)
```

```{r}
summary(expired_subs$expire_after_specific_number_of_charges)
summary(as.factor(expired_subs$order_interval_frequency))/nrow(expired_subs)
```

```{r}
# start date
expired_subs$start_date = as.Date(strptime(expired_subs$created_at, "%Y-%m-%d"))
expired_subs$start_hour = as.numeric(format(strptime(expired_subs$created_at, "%Y-%m-%d %H:%M:%S"), "%H"))
# cancellation date
expired_subs$end_date = as.Date(strptime(expired_subs$cancelled_at, "%Y-%m-%d"))
expired_subs$end_hour = as.numeric(format(strptime(expired_subs$cancelled_at, "%Y-%m-%d %H:%M:%S"), "%H"))
# difference in days
expired_subs$sub_length_in_days = as.numeric(expired_subs$end_date-expired_subs$start_date)
```


Summary statistics for length of expired subscriptions:
```{r}
values = subset(expired_subs, !is.na(end_date))
summary(values$sub_length_in_days)
boxplot(values$sub_length_in_days, main="Boxplot: sub length in days for subs with status=EXPIRED")
hist(values$sub_length_in_days, main="Histogram: sub length in days for subs with status=EXPIRED")
```





# Cancelled subs
```{r}
cancelled_subs = subset(subscriptions_dataset, status == "CANCELLED")
str(cancelled_subs)
```

```{r}
# start date
cancelled_subs$start_date = as.Date(strptime(cancelled_subs$created_at, "%Y-%m-%d"))
cancelled_subs$start_hour = as.numeric(format(strptime(cancelled_subs$created_at, "%Y-%m-%d %H:%M:%S"), "%H"))
summary(cancelled_subs$start_date)
summary(cancelled_subs$start_hour)
# cancellation date
cancelled_subs$end_date = as.Date(strptime(cancelled_subs$cancelled_at, "%Y-%m-%d"))
cancelled_subs$end_hour = as.numeric(format(strptime(cancelled_subs$cancelled_at, "%Y-%m-%d %H:%M:%S"), "%H"))
summary(cancelled_subs$end_date)
summary(cancelled_subs$end_hour)
# difference in days
cancelled_subs$sub_length_in_days = as.numeric(cancelled_subs$end_date-cancelled_subs$start_date)
```

# Summary statistics for cancelled subs
```{r}
summary(cancelled_subs$sub_length_in_days)
boxplot(cancelled_subs$sub_length_in_days, main="Boxplot: sub length in days for subs with status=CANCELLED")
hist(cancelled_subs$sub_length_in_days, main="Histogram: sub length in days for subs with status=CANCELLED")
```

# Active subs
```{r}
active_subs = subset(subscriptions_dataset, status == "ACTIVE")
str(active_subs)
```

```{r, transform dates}
# start date
active_subs$start_date = as.Date(strptime(active_subs$created_at, "%Y-%m-%d"))
active_subs$start_hour = as.numeric(format(strptime(active_subs$created_at, "%Y-%m-%d %H:%M:%S"), "%H"))
# difference in days
active_subs$sub_length_in_days = as.numeric(as.Date("2020-04-30")-active_subs$start_date)
```

## Summary statistics for cancelled subs
```{r}
summary(active_subs$sub_length_in_days)
boxplot(active_subs$sub_length_in_days, main="Boxplot: sub length in days for subs with status=ACTIVE")
hist(active_subs$sub_length_in_days, main="Histogram: sub length in days for subs with status=ACTIVE")
```




# **CUSTOMER** level
```{r}
# aggregate(df$date2,by=list(df$id),max)
subscriptions_dataset$created_at = as.Date(strptime(subscriptions_dataset$created_at, "%Y-%m-%d"))
subscriptions_dataset$cancelled_at = as.Date(strptime(subscriptions_dataset$cancelled_at, "%Y-%m-%d"))
customer_start_date = aggregate(subscriptions_dataset$created_at, by=list(subscriptions_dataset$customer_id), min)
names(customer_start_date) = c("customer_id", "customer_start_date")
customer_end_date = aggregate(subscriptions_dataset$cancelled_at, by=list(subscriptions_dataset$customer_id), max)
names(customer_end_date) = c("customer_id", "customer_end_date")
customer_start_end_date = merge(customer_start_date, customer_end_date, by="customer_id")
customer_start_end_date$diff =as.numeric( customer_start_end_date$customer_end_date-customer_start_end_date$customer_start_date)
values = subset(customer_start_end_date, !is.na(diff))
```

```{r}
summary(values$diff)
```


