---
title: 'Question 6: Which product would you advertise the most to new users?'
author: "Kristina Maceković"
date: "5/7/2020"
output: html_document
---
```{r, echo=FALSE}
# Check working directory
Sys.setlocale("LC_ALL","English")
getwd()
#setwd(paste(getwd(), "/Documents/jobs/jobs2020/lebesgue-test-exercise", sep=""))
```

```{r, import data, echo=FALSE}
line_items_dataset = read.csv("./init_data/line_items.csv")
subscriptions_dataset = read.csv("./init_data/subscriptions.csv")
```

```{r, echo=FALSE}
str(line_items_dataset)
str(subscriptions_dataset)
```

# What is the most common price for each product?

Looking at the subscription data:
```{r}
with(subscriptions_dataset, tapply(price, product_title, summary))
#product_price_per_quantity_item = aggregate(line_items_dataset$price, by=list(line_items_dataset$product_title, line_items_dataset$quantity), mean)
#names(product_price_per_quantity_item) = c("product", "quantity", "price")
```

Looking at the line items data:
```{r}
with(line_items_dataset, tapply(price, product_title, summary))
```

Also looked on a per-quantity, per-frequency basis, but didn't have a difference.

The most common prices:

- dark chocolate: 40$
- milk chocolate: 33$
- white chocolate: 33$

# What is the most common product in active subs?

In all active subs:
```{r, echo=FALSE}
active_subs = subset(subscriptions_dataset, status == "ACTIVE")
tbl = with(active_subs, data.frame(table(product_title)/nrow(active_subs)))
tbl = tbl[order(-tbl$Freq), ]
tbl
```

In active subs longer than 2M:
```{r, echo=FALSE}
# define length of sub
active_subs$sub_length_in_days = as.numeric(as.Date("2020-04-30") - as.Date(format(strptime(active_subs$created_at, "%Y-%m-%d %H:%M:%S"), "%Y-%m-%d")))
long_active_subs = subset(active_subs, sub_length_in_days > 60)
tbl = with(long_active_subs, data.frame(table(product_title)/nrow(long_active_subs)))
tbl = tbl[order(-tbl$Freq), ]
tbl
```

In active subs longer than 6M:
```{r, echo=FALSE}
# define length of sub
long_active_subs = subset(active_subs, sub_length_in_days > 180)
tbl = with(long_active_subs, data.frame(table(product_title)/nrow(long_active_subs)))
tbl = tbl[order(-tbl$Freq), ]
tbl
```

Prices in long active subs:
```{r}
mn = with(long_active_subs, aggregate(price, by=list(product_title), min))
mx = with(long_active_subs, aggregate(price, by=list(product_title), max))
avg = with(long_active_subs, aggregate(price, by=list(product_title), mean))
med = with(long_active_subs, aggregate(price, by=list(product_title), median))
mn
mx
avg
med
```


# What is the least common product in cancelled or expired subs?
```{r, echo=FALSE}
cancelled_subs = subset(subscriptions_dataset, status == "CANCELLED")
tbl = with(cancelled_subs, data.frame(table(product_title)/nrow(cancelled_subs)))
tbl = tbl[order(-tbl$Freq), ]
tbl
```

# What are the reasons for cancellation?
```{r}
all_reasons = data.frame(table(cancelled_subs$cancellation_reason)/nrow(cancelled_subs))

# milk
milk = subset(cancelled_subs, product_title=="Milk Chocolate 10.00% Off Auto renew")
milk_reasons = data.frame(with(milk, table(cancellation_reason)/nrow(milk)))
names(milk_reasons) = c("reason", "milk_freq")

# dark
dark = subset(cancelled_subs, product_title=="Dark Chocolate 10.00% Off Auto renew")
dark_reasons = data.frame(with(dark, table(cancellation_reason)/nrow(dark)))
names(dark_reasons) = c("reason", "dark_freq")

# white
white = subset(cancelled_subs, product_title=="White Chocolate 10.00% Off Auto renew")
white_reasons = data.frame(with(white, table(cancellation_reason)/nrow(white)))
names(white_reasons) = c("reason", "white_freq")

reasons = merge(milk_reasons, dark_reasons, by="reason")
reasons = merge(reasons, white_reasons, by="reason")
```

```{r}
reasons[order(-reasons$milk_freq),]
```

# Which variant is the most popular in long active subs?
```{r}
df = data.frame(table(long_active_subs$variant_title))
df = df[order(-df$Freq),]
df
```

# Which variant in milk chocolate is the most popular?
```{r}
active_milk = subset(active_subs, product_title == "Milk Chocolate 10.00% Off Auto renew")
df = data.frame(table(active_milk$variant_title))
df = df[order(-df$Freq), ]
df
```

# Which variant in dark chocolate is the most popular?
```{r}
active_dark = subset(active_subs, product_title == "Dark Chocolate 10.00% Off Auto renew")
df = data.frame(table(active_dark$variant_title))
df = df[order(-df$Freq), ]
df
```

# What is the most common cancelled variant?
```{r}
df = data.frame(table(cancelled_subs$variant_title))
df = df[order(-df$Freq),]
df
```


# Ratio of active over cancelled subs for each product
```{r}
long_active_subs = subset(active_subs, sub_length_in_days > 60)
cancelled_subs$sub_length_in_days = as.numeric(as.Date(format(strptime(cancelled_subs$cancelled_at, "%Y-%m-%d %H:%M:%S"), "%Y-%m-%d")) - as.Date(format(strptime(cancelled_subs$created_at, "%Y-%m-%d %H:%M:%S"), "%Y-%m-%d")))
long_cancelled_subs = subset(cancelled_subs, sub_length_in_days > 60)



num_active = data.frame(table(long_active_subs$product_title)/nrow(long_active_subs))
names(num_active) = c("Product", "num_active")
num_cancelled = data.frame(table(long_cancelled_subs$product_title)/nrow(long_cancelled_subs))
names(num_cancelled) = c("Product", "num_cancelled")
ratio_active_cancelled_per_product = merge(num_active, num_cancelled, by="Product")
ratio_active_cancelled_per_product$ratio = ratio_active_cancelled_per_product$num_active/ratio_active_cancelled_per_product$num_cancelled
```

```{r}
ratio_active_cancelled_per_product[order(-ratio_active_cancelled_per_product$ratio),]
```


# The same, but for variants
```{r}
num_active = data.frame(table(long_active_subs$variant_title)/nrow(long_active_subs))
names(num_active) = c("Variant", "num_active")

num_cancelled = data.frame(table(long_cancelled_subs$variant_title)/nrow(long_cancelled_subs))
names(num_cancelled) = c("Variant", "num_cancelled")

ratio_active_cancelled_per_variant = merge(num_active, num_cancelled, by="Variant")

ratio_active_cancelled_per_variant$ratio = ratio_active_cancelled_per_variant$num_active/ratio_active_cancelled_per_variant$num_cancelled
```

```{r}
ratio_active_cancelled_per_variant[order(-ratio_active_cancelled_per_product$ratio),]
```

## Reasons for cancellation in this sample
```{r}
# milk
milk = subset(long_cancelled_subs, product_title=="Milk Chocolate 10.00% Off Auto renew")
milk_reasons = data.frame(with(milk, table(cancellation_reason)/nrow(milk)))
names(milk_reasons) = c("reason", "milk_freq")

# dark
dark = subset(long_cancelled_subs, product_title=="Dark Chocolate 10.00% Off Auto renew")
dark_reasons = data.frame(with(dark, table(cancellation_reason)/nrow(dark)))
names(dark_reasons) = c("reason", "dark_freq")

# white
white = subset(long_cancelled_subs, product_title=="White Chocolate 10.00% Off Auto renew")
white_reasons = data.frame(with(white, table(cancellation_reason)/nrow(white)))
names(white_reasons) = c("reason", "white_freq")

reasons = merge(milk_reasons, dark_reasons, by="reason")
reasons = merge(reasons, white_reasons, by="reason")
```

```{r}
reasons[order(-reasons$milk_freq),]
```



```{r}
variant_cancellation_reason = data.frame(with(long_cancelled_subs, table(variant_title, cancellation_reason)/nrow(long_cancelled_subs)))
variant_cancellation_reason[order(-variant_cancellation_reason$Freq),]
doesnt_like = subset(variant_cancellation_reason, cancellation_reason == "I don't like the product" | cancellation_reason=="I want a different product or variety" | cancellation_reason=="This is too expensive")
doesnt_like[order(-doesnt_like$Freq),]
```

# "Other reason" Analysis
```{r}
reason_description = subscriptions_dataset$cancellation_reason_comment
reason_description = reason_description[reason_description != "NULL" &  reason_description != ""]
str(reason_description)
all_together = paste(reason_description, collapse = " ")
#all_together
lowercase = tolower(all_together)
#lowercase
```

```{r}
# Install
install.packages("tm")  # for text mining
install.packages("SnowballC") # for text stemming
install.packages("wordcloud") # word-cloud generator 
install.packages("RColorBrewer") # color palettes
# Load
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
```


```{r}
docs <- Corpus(VectorSource(lowercase))
```

```{r}
#inspect(docs)
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, "", x))
docs <- tm_map(docs, toSpace, "\n")
# Remove english common stopwords
docs <- tm_map(docs, removeWords, stopwords("english"))
# Remove punctuations
docs <- tm_map(docs, removePunctuation)
# Eliminate extra white spaces
docs <- tm_map(docs, stripWhitespace)
```
```{r}
inspect(docs)
```



```{r}
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
head(d, 10)
```

Wordcloud
```{r}
set.seed(1234)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

Frequent words:
```{r}
findFreqTerms(dtm, lowfreq = 10)
```

Barplot of the most frequent words:
```{r}
barplot(d[1:10,]$freq, las = 2, names.arg = d[1:10,]$word
        , main ="Most frequent words",
        ylab = "Word frequencies")
```

```{r}
like_reasons = reason_description[grepl("like", reason_description, ignore.case = TRUE)]
head(like_reasons, 10)
```
```{r}
product_reasons = reason_description[grepl("product", reason_description, ignore.case = TRUE)]
head(product_reasons, 10)
```

```{r}
sub_reasons = reason_description[grepl("subscription", reason_description, ignore.case = TRUE)]
head(sub_reasons, 10)
```

```{r}
choco_reasons = reason_description[grepl("chocolate", reason_description, ignore.case = TRUE)]
head(choco_reasons, 10)
```

```{r}
order_reasons = reason_description[grepl("order", reason_description, ignore.case = TRUE)]
head(order_reasons, 10)
```


```{r}
choco_or_not_like = subscriptions_dataset[grepl("don't like", subscriptions_dataset$cancellation_reason_comment, ignore.case = TRUE),]
df = data.frame(table(choco_or_not_like$variant_title)/nrow(choco_or_not_like))
df[order(-df$Freq),]
```


